### 2022-06-13 main/chapter_2ljets.tex
\atlas\

Before that redesign, an multi-jet signal region SR-Low-ISR was included,
with associated validation and control regions,
which required $\njet \geq 3$ and offered some meagre extra sensitivity.
Here, `ISR' stands for Initial-State Radiation, following the naming
of previous \atlas searches including partial Run-2 2/3-lepton
search which we are updating~\cite{atlas_23l_SUSY_2016_24}.

@@

This complication is a great deal of cost for what is only a weakly sensitive
signal region, reaching only a projected significance $Z\approx 1$ for the
(pre-fit) signals shown in Figure~\ref{fig:2ljets_low_isr_old_sr}.
On the very sound advice of \atlas authors commenting on the internal
documentation, this ISR construction was entirely removed.

>>>>

Before that redesign, an multi-jet signal region SR-Low-ISR was included,
with associated validation and control regions,
which required $\njet \geq 3$ and offered some meagre extra sensitivity.
Here, `ISR' stands for Initial-State Radiation, following the naming
of previous \atlas\ searches including partial Run-2 2/3-lepton
search which we are updating~\cite{atlas_23l_SUSY_2016_24}.

@@

This complication is a great deal of cost for what is only a weakly sensitive
signal region, reaching only a projected significance $Z\approx 1$ for the
(pre-fit) signals shown in Figure~\ref{fig:2ljets_low_isr_old_sr}.
On the very sound advice of \atlas\ authors commenting on the internal
documentation, this ISR construction was entirely removed.
